Precise Spiking Motifs in Neurobiological and Neuromorphic~Data

### 2022-12-28 2022-12-28_coverletter.tex
Update 2022-12-28_coverletter.tex

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
Many thanks for accepting our manuscript entitled ``Precise spiking motifs in neurobiological and neuromorphic data'' for your consideration as a review paper in \emph{Brain Sciences}. We are very grateful to the reviewers for their very insightful remarks and we have now responded to all their remarks.

We have accepted all changes suggested at the proofreading stage and uploaded our files on the MDPI website.

\textbf{ Note that in agreement with the editorial office, we have added Jean-Nicolas Jérémie as an author, as his contributions were substantial for writing this review.}

@@

This is an invited Feature Paper, with a full waiver on the APC. In addition, all the python code needed to reproduce figures and supplementary materials will be fully open-source

>>>>

%----------------------------------------------------------------------------------------
%	LETTER CONTENT
%----------------------------------------------------------------------------------------
Many thanks for accepting our manuscript entitled ``Precise spiking motifs in neurobiological and neuromorphic data'' for publication as a review paper in \emph{Brain Sciences}. We have accepted all changes suggested at the proofreading stage and uploaded our files on the MDPI website.

@@

This is an invited Feature Paper, with a full waiver on the APC. In addition, all the python code needed to reproduce figures and supplementary materials will be fully open-source.
